Approximation as Differentiation

### 2025-06-09 main/first-order.tex
Clarify CMon monoidal.

For differentiable functions, we can combine linear approximations by adding tangent vectors. For stable
functions, we can combine approximants by taking their meet. The additive structure in both cases form a
commutative monoid with an addition + and zero element 0. A category $\cat{C}$ is enriched in $\CMon$, the
category of commutative monoids, when every hom-set $\cat{C}(X,Y)$ has a similar additive structure, providing
an operation + to add morphisms together plus a zero morphism $0: X \to Y$, and composition is
\emph{bilinear}, i.e.~given by a family of morphisms $\Hom{\cat{C}}{Y}{Z} \tensor \Hom{\cat{C}}{X}{Y} \to
\Hom{\cat{C}}{X}{Z}$ in $\CMon$ that preserve the additive structure in $\Hom{\cat{C}}{Y}{Z}$ and
$\Hom{\cat{C}}{X}{Y}$ separately:

@@

@@

\subsubsection{Biproduct laws}
It is also easy to show that in a semi-additive category the following equations hold:
%\vspace{-4mm}
\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{salign*}
   \biproj_X \comp \biinj_X &= \id_X \\
   \biproj_Y \comp \biinj_X &= \zero_{X,Y}
\end{salign*}
\end{center}
\end{minipage}%
\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{salign*}
   \biproj_Y \comp \biinj_Y &= \id_Y \\
   \biproj_X \comp \biinj_Y &= \zero_{Y,X}
\end{salign*}
\end{center}
\end{minipage}

\vspace{3mm}
\noindent It is also possible to use these laws to define biproducts, in the case where $\cat{C}$ is enriched
in $\CMon$ and so equipped with addition of morphisms and zero morphisms. In that case any products or
coproducts in $\cat{C}$ are necessarily biproducts.

>>>>

For differentiable functions, we can combine linear approximations by adding tangent vectors. For stable
functions, we can combine approximants by taking their meet. The additive structure in both cases form a
commutative monoid with an addition + and zero element 0. A category $\cat{C}$ is enriched in $\CMon$, the
(monoidal) category of commutative monoids, when every hom-set $\cat{C}(X,Y)$ provides an operation + to add
morphisms together plus a zero morphism $0: X \to Y$, and composition is \emph{bilinear}, i.e.~given by a
family of morphisms $\Hom{\cat{C}}{Y}{Z} \tensor \Hom{\cat{C}}{X}{Y} \to \Hom{\cat{C}}{X}{Z}$ in $\CMon$ that
preserve the additive structure in $\Hom{\cat{C}}{Y}{Z}$ and $\Hom{\cat{C}}{X}{Y}$ separately:

@@

\subsubsection{Biproducts}

In any $\CMon$-category,

\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{salign*}
   \biproj_X \comp \biinj_X &= \id_X \\
   \biproj_Y \comp \biinj_X &= \zero_{X,Y}
\end{salign*}
\end{center}
\end{minipage}%
\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{salign*}
   \biproj_Y \comp \biinj_Y &= \id_Y \\
   \biproj_X \comp \biinj_Y &= \zero_{Y,X}
\end{salign*}
\end{center}
\end{minipage}

\hrule

@@

\subsubsection{Biproduct laws}

It is also possible to use these laws to define biproducts, in the case where $\cat{C}$ is enriched
in $\CMon$ and so equipped with addition of morphisms and zero morphisms. In that case any products or
coproducts in $\cat{C}$ are necessarily biproducts.
